Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-07 documentation/paper.tex
Added statistic for number of examples on gravitational differentiation

As seen in Figure \ref{grav_acc_by_hyper}, all 3 hyperparameters that were optimized during the grid search had a significant effect on accuracy:
\begin{itemize}
    \item Smaller gravitational multipliers improved performance; the best value tested was 0.0005. This implies that the gravity effect on each unlabeled event should be weighted lightly compared to the labeled examples.
    \item Higher learning rates improve performance, with the best value tested at a quite high 0.03.
    \item Larger distortion powers (which raise the confidence threshold for a significant gravitational effect) improved performance, with the best tested at 11.
\end{itemize}

@@

>>>>

As seen in Figure \ref{grav_acc_by_hyper}, all 3 hyperparameters that were optimized during the grid search had a significant effect on accuracy:

\begin{itemize}
    \item Smaller gravitational multipliers improved performance; the best value tested was 0.0005. This implies that the gravity effect on each unlabeled event should be weighted lightly compared to the labeled examples.
    \item Higher learning rates improve performance, with the best value tested at a quite high 0.03.
    \item Larger distortion powers (which raise the confidence threshold for a significant gravitational effect) improved performance, with the best tested at 11.
\end{itemize}

@@

Two different options were tested with regard to size of the labeled data set $\varsigma$. Out of a set of 496 total examples available for training, either 128 (approximately $1/4$ of the total set) or 256 (approximately $1/2$) were used as labeled data. Over the entire grid search, runs with 128 examples in $\varsigma$ produced on average 64\% more errors on validation data, compared to those with 256 examples.
